\chapter{Recommendations}
\label{cp:recommendations}

\section{For the Nigerian Economic Advisory Team}

\begin{enumerate}
	\item \textbf{Foreign Exchange Intervention for Essential Industries:}  
	Implement a \textbf{``Managed Floating Window''}---a dedicated and prioritized foreign exchange channel for essential industrial inputs. This approach would mitigate the value erosion experienced by FX-exposed firms such as Nestlé Nigeria and MTN Nigeria by reducing exchange rate volatility on critical imports.
	
	\item \textbf{Agricultural Productivity and Value Addition:}  
	Shift policy focus from subsistence farming toward \textbf{agro-processing and value-chain development}. Strategic investment in secure transportation corridors and solar-powered cold storage infrastructure would reduce post-harvest losses, stabilize food supply, and moderate food inflation.
	
	\item \textbf{Temporary Windfall Tax on Revaluation Gains:}  
	Introduce a temporary \textbf{``Windfall Tax''} on extraordinary banking-sector profits arising from foreign exchange revaluation gains. Proceeds should be earmarked for infrastructure and credit support in struggling real-sector industries.
\end{enumerate}

\section{For Investors}

\begin{itemize}
	\item \textbf{Overweight: Financial Services (Tier-1 Banks).}  
	Tier-1 banks---particularly \textbf{Zenith Bank}---offer the most effective hedge against Naira volatility and sustained high-interest-rate environments due to strong capital buffers and revaluation gains.
	
	\item \textbf{Overweight: Upstream Energy.}  
	\textbf{Seplat Energy} provides exposure to the Nigerian economy with implicit \textbf{hard-currency protection}, as revenues are largely dollar-denominated, insulating earnings from domestic currency depreciation.
	
\item \textbf{Avoid: Highly Leveraged Consumer Goods Firms.}  
	Until exchange rate stability improves, highly leveraged consumer goods companies are likely to continue recording \textbf{accounting losses} driven by foreign exchange liabilities, limiting dividend capacity and equity returns.
\end{itemize}
